A systematic search for transiting planets in the \KT\ data

### 2015-02-15 ms.tex
few tweaks

To test the performance and detection efficiency of our method, we conducted a
suite of XXXX injection and recovery tests, this is the result of 5 tests per
star.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting light curve
through the full pipeline.
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search---with period and reference transit time within
HOWMANY days of the injected signal, we count that injection as recovered.
The detection efficiency of the search is approximately given by the fraction
of recovered injections as a function of the relevant parameters.

>>>>

To test the performance and detection efficiency of our method, we conducted a
suite of \dfmtodo{XXXX} injection and recovery tests, five tests per
target star.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting injected light curve
through the full pipeline (except the manual vetting).
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search---with period and reference transit time within
\dfmtodo{HOWMANY~days} of the injected signal, we count that injection as recovered.
The detection efficiency of the search is given approximately by the fraction
of recovered injections as a function of the relevant parameters.
